Semi-Permeable Vesicles: Mathematical Formulation, Numerics, and Physics

### 2020-10-22 vesicle_code/docs/permeableVes/main.tex
putting in contant pressure drop

%\usepgfplotslibrary{external}
%\tikzexternalize

@@

@@

\begin{figure*}[htp]
  \centering
%  \input{figures/ellipseVelocity1.tikz}
%  \input{figures/ellipseVelocity2.tikz}
%  \input{figures/ellipseVelocity3.tikz}
%  \input{figures/ellipseVelocityNorms.tikz}
  \includegraphics[width=0.24\linewidth]{figures/ellipseVelocity1.pdf}
  \includegraphics[width=0.24\linewidth]{figures/ellipseVelocity2.pdf}
  \includegraphics[width=0.24\linewidth]{figures/ellipseVelocity3.pdf}
  \includegraphics[width=0.24\linewidth]{figures/ellipseVelocityNorms.pdf}
  \caption{\label{fig:vesVelocity} The velocity contributions due to
  force balance (blue) and permeability (red). The green line is the
  velocity of an impermeable vesicle with the same initial shape as the
  semi-permeable vesicle. The right-most plot is the maximum norm of
  each velocity contribution. The black lines correspond to the times
  reported in the other three plots.}
\end{figure*}

>>>>

\usepgfplotslibrary{external}
\tikzexternalize

@@

\begin{figure*}[htp]
  \centering
  \begin{minipage}{0.4\textwidth}
  \includegraphics[width=\linewidth]{figures/ellipseArea}
  \end{minipage}
  \hfill
  \begin{minipage}{0.56\textwidth}
  \includegraphics[width=0.31\linewidth]{figures/ellipseVelocity1.pdf}
  \includegraphics[width=0.31\linewidth]{figures/ellipseVelocity2.pdf}
  \includegraphics[width=0.31\linewidth]{figures/ellipseVelocity3.pdf}
  \end{minipage}
  \caption{A big caption for a composite figure}
\end{figure*}

@@

\begin{figure*}[htp]
  \centering
%  \scalebox{0.6}{\input{figures/ellipseVelocity1.tikz}}
%  \scalebox{0.6}{\input{figures/ellipseVelocity2.tikz}}
%  \scalebox{0.6}{\input{figures/ellipseVelocity3.tikz}}
%  \scalebox{0.6}{\input{figures/ellipseVelocity4.tikz}}
%  \input{figures/ellipseVelocityNorms.tikz}
  \includegraphics[width=0.24\linewidth]{figures/ellipseVelocity1.pdf}
  \includegraphics[width=0.24\linewidth]{figures/ellipseVelocity2.pdf}
  \includegraphics[width=0.24\linewidth]{figures/ellipseVelocity3.pdf}
  \includegraphics[width=0.24\linewidth]{figures/ellipseVelocity4.pdf}
  \caption{\label{fig:vesVelocity} The normal velocity contributions due
  to force balance (blue) and permeability (red). The green line is the
  velocity of an impermeable vesicle with the same initial shape as the
  semi-permeable vesicle.}
\end{figure*}
